---
title: "Tidymodels packages in R"
author: "Bilikisu W. Aderinto"
date: "11/24/2020"
output: 
    html_document: 
      toc: true
      toc_depth: 2
      toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tidymodels packages in R

The tidymodels framework is **a collection of packages** for **modeling and machine learning** using [tidyverse](https://www.tidyverse.com) principles. [Tidymodels, 2020](https://www.tidymodels.org)

```{r}
library(tidymodels)
```


```{r, warning=FALSE, error=FALSE, message=FALSE}
library(tidyverse)
library(themis)
library(knitr)
library(skimr)

#library(ranger)
#library(randomForest)
```

## Read Data into workspace

```{r, warning=FALSE, error=FALSE, message=FALSE}
bankmarketing_data <- read_csv("bankmarketing_train.csv")
```

```{r}
glimpse(bankmarketing_data)
```

## Data Summary

```{r, results='hide'}
skim(bankmarketing_data)
```


## Data Cleaning and Data manipulation

```{r}
bankmarketing_cleaned <- bankmarketing_data %>% 
  mutate_if(is.character, factor) 

glimpse(bankmarketing_cleaned)
```


## Modeling

### rsample package - Data Sampling

1. split dataset
`initial_split()` creates a single binary split of the data into a training set and testing set.
```{r}
set.seed(923)
bankmarketing_split <- initial_split(bankmarketing_cleaned, strata = y)

#bankmarketing_split <- initial_split(bankmarketing_cleaned, prop = 0.7)

bankmarketing_split
```

2. get the training and testing data

`training()` and `testing()` are used to extract the resulting data.
```{r}
bankmarketing_train <- training(bankmarketing_split)
```

```{r}
bankmarketing_train %>% 
  count(y)
```


```{r}
bankmarketing_test <- testing(bankmarketing_split)
```

```{r}
bankmarketing_test %>% 
  count(y)
```


```{r}
set.seed(123)
bm_boot <- bootstraps(bankmarketing_train)
bm_boot
```


```{r}
ranger_spec <- rand_forest() %>%
  set_mode("classification") %>%
  set_engine("ranger")

ranger_spec
```


```{r}
rf_spec <- rand_forest() %>%
  set_mode("classification") %>%
  set_engine("randomForest")

rf_spec
```


```{r}
bm_workflow <- workflow() %>%
  add_formula(y ~ .)

bm_workflow
```


```{r}
ranger_results <- bm_workflow %>%
  add_model(ranger_spec) %>%
  fit_resamples(
    resamples = bm_boot,
    control = control_resamples(save_pred = TRUE)
  )

ranger_results
```


```{r}
rf_results <- bm_workflow %>%
  add_model(rf_spec) %>%
  fit_resamples(
    resamples = bm_boot,
    control = control_resamples(save_pred = TRUE)
  )

rf_results
```


### Evaluate Models
Now let’s check out performance of each model using the `tune` package.

```{r}

collect_metrics(rf_results)
```


```{r}
collect_metrics(ranger_results) # tune package
```


```{r}
ranger_results %>%
  conf_mat_resampled() # tune package
```


```{r}
rf_results %>% 
  conf_mat_resampled() # tune package
```


```{r}
# collect predictions for the ranger model
ranger_results %>% 
  collect_predictions() # tune package
```



```{r}
ranger_results %>%
  collect_predictions() %>%
  group_by(id) %>% # to get out 25 ROC curves
  roc_curve(y, .pred_yes) %>%
  #autoplot() %>% # tune package
  ggplot(aes(1 - specificity, sensitivity, color = id)) +
  geom_abline(lty = 2, color = "gray80", size = 1.5) +
  geom_path(show.legend = FALSE, alpha = 0.6, size = 1.2) +
  coord_equal()


```


```{r}
bm_final <- bm_workflow %>%
  add_model(ranger_spec) %>%
  last_fit(bankmarketing_split)

bm_final
```

```{r}
collect_metrics(bm_final)
```

```{r}
collect_predictions(bm_final) %>%
  conf_mat(y, .pred_class)
```

